Title Goes Here

### 2020-01-30 paper/paper.tex
More on ProdMatch
Started to describe 'construct'

\ttt{ProdMatch s t} is equivalent to a function a curried function from \ttt{s} to \ttt{t}.
Note that \ttt{s} will be a (potentially nested) pair type.

>>>>

\ttt{ProdMatch s t} is equivalent to a function a curried function from \ttt{s} to \ttt{t}.
Note that \ttt{s} will be a (potentially nested) pair type. For example,
\ttt{ProdMatch (a, (b, c)) r} will be equivalent to \ttt{a -> b -> c -> r}.

\begin{lstlisting}
data ProdMatch s t where
  ProdMatch ::
    (ERep a, ERep b)
      => (E a -> ProdMatch b r) -> ProdMatch (a, b) r

  OneProdMatch :: ERep a => (E a -> E r) -> ProdMatch a r

  NullaryMatch :: ERep r => E r -> ProdMatch a r
\end{lstlisting}

\section{Constructing values}

\begin{lstlisting}
construct ::
  Construct (a -> b)
    => (a -> b) -> LiftedFn (a -> b)
construct = construct' . Construct

-- Example: LiftedFn (a -> b -> c) is: E a -> E b -> E c
type family LiftedFn t where
  LiftedFn (a -> b) = E a -> LiftedFn b
  LiftedFn b = E b

class Construct t where
  construct' :: E t -> LiftedFn t
\end{lstlisting}

Example GHCi session, demonstrating \ttt{construct}:

\begin{lstlisting}
ghci> :t construct (,)
construct (,)
  :: (ERep a, ERep b) => E a -> E b -> E (a, b)

ghci> :t construct (,,)
construct (,,)
  :: (ERep a, ERep b, ERep c) =>
     E a -> E b -> E c -> E (a, b, c)

ghci> :t construct (,,) (rep False) (rep 3.1 :: E Double) (rep 1 :: E Int)
construct (,,) (rep False) (rep 3.1 :: E Double) (rep 1 :: E Int)
  :: E (Bool, Double, Int)
\end{lstlisting}
